---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width = 6, fig.height = 4)
library(tidyverse)
dane <- read_csv("Data/previous_application_new.csv")
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Intro

The purpose of this project is to analyze previous application data to extract insights that can help in understanding customer behavior and improving decision-making processes.

## Research Questions

1.  First question
2.  Second question

## Braki danych

```{r}
naniar::vis_miss(dane)
library(VIM)
aggr(dane, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, labels=names(dane), cex.axis=.7, gap=3, ylab=c("Procent braków danych","Wzorzec braków danych"))
```
